MinCall --- MinION basecaller model pogonjen dubokim učenjem

### 2017-05-14 paper/main.tex
Update

Although MinION is able to produce long reads, they have a high sequencing error rate. This has been somewhat alleviated with new R9 pore model, replacing older R7 ones. In this paper, we show that this error rate can be reduced by replacing the default base caller provided by the manufacturer with a properly trained neural network model. In the future new R9.5 chemistry and 1D^2 reads supersede current models.

@@

\subsection{E.Coli perfomnace}

TODO

See \url{https://github.com/nmiculinic/minion-basecaller/blob/master/notebook/Lambda_nanonet_vs_m270.ipynb for preliminary results.}

>>>>

Although MinION is able to produce long reads, they have a high sequencing error rate. This has been somewhat alleviated with new R9 pore model, replacing older R7 ones. In this paper, we show that this error rate can be reduced by replacing the default base caller provided by the manufacturer with a properly trained neural network model. In the future new R9.5 chemistry and 1D\^2 reads supersede current models.

@@

\subsection{Performance tables}

As decribed in previous section, model was tested on E.Coli test set and compared to open source Nanonet and Albacore. Albacore doesn't have specific R9 chemistry mode, thus R9.4 was used instead which explains its lower perfomances on this task. Results are in \ref{table:1}

\begin{table}[h!]
\centering
\begin{tabular}{lrrrrrrr}
\toprule
{} &  Deletion rate &  Error rate &  Insertion rate &  Match rate &  Mismatch rate &  Read length\\
\midrule
albacore     &       0.060 &    0.194 &        0.070 &    0.867 &       0.063 &  9843 \\
nanonet      &       0.088 &    0.190 &        0.040 &    0.897 &       0.062 &  5029 \\
mincall\_m270 &       0.077 &    0.172 &        0.040 &   0.905 &       0.056 &  9378 \\
\bottomrule
\end{tabular}

\caption{Mean performance metrics on E.Coli dataset, 5k sample}
\label{table:1}
\end{table}

We also tested and compared models on Human genome~\cite{jain2017nanopore} chromosone Y with R9.4 chemistry. Our model was only trained on R9 chemisty which explain drop in perfomance compared to Albacore. In our tests Nanonet produces significantly shorted read then data length and generally unusable perfomance on this dataset despite supporting R9.4 chemisty used in dataset.
